Factors determining how catchments respond to forest cover change. Re-analysing global data sets.

### 2022-04-01 paper/Forest_and_Water/Forest_and_Water.Rmd
fixed errors in pdf and added cover letter

This model explains more of the variance, but the improvement is marginal compared to the previous model with a adjusted *r^2^* of `r round(summary(model6_all)$r.sq,2)`. This indicates that the categorical variables explain a limited amount of the overall variance in the change in flow data. However, it is interesting to note from Table \@ref(tab:msix-linear) that several of the assessment methods are significant. In particular Paired Watersheds experiments (PWE), Hydrological modelling (HM) and Statistical techniques (SH) are strongly significant ($p < 0.05$). 
In this case, *log10(Area (km^2^))* is no longer a significant predictor, the reasons for this will be discussed later.

@@

```{r smoothsmodel6, fig.cap="Visualisation of the smooth variables in the model. The shaded areas are the 95% confidence intervals associated with the fit of the smooth, the blue line is the mean smoothed relationshiop. The data are plotted as individual points", out.width="90%", echo=F}

include_graphics("model6_smooths.png")
```

@@

This last model has more explaining power with an adjusted *r^2^* of `r round(summary(model7)$r.sq,2)`. * The results indicate that *Dryness* indicates a clear signifcant non-linear response where changes in forest cover in drier catchments having a greater impact on streamflow (Figure \@ref(fig:smoothsmodel7)). Catchment area (*log10(Area (km^2^))*) also shows reasonable evidence of having an impact on flow with p = `r round(summary(model7)$s.table[2,4],2)`, and suggesting once again that changes in forest cover in larger catchments have less impact on streamflow. The variable *length* no longer is significant, after removal of the two studies with very long lengths.

@@

One concern with the result presented heer, is that there are a few assessment techniques in the original dataset with a very low number of observations and this might skew the results of the analysis. This includes the category of Quasi paired watersheds and combinations of elasticity analysis and hydrological modelling (EA,HM) and paired watersheds and hydrological modelling (PWE,HM) (Table \@ref(tab:tableassess) and Figure \@ref(fig:assessment)).

>>>>

This model (Tables \@ref(tab:msix-linear) and \@ref(tab:msix-smooth)) explains more of the variance, but the improvement is marginal compared to the previous model with a adjusted *r^2^* of `r round(summary(model6_all)$r.sq,2)`. This indicates that the categorical variables explain a limited amount of the overall variance in the change in flow data. However, it is interesting to note from Table \@ref(tab:msix-linear) that several of the assessment methods are significant. In particular Paired Watersheds experiments (PWE), Hydrological modelling (HM) and Statistical techniques (SH) are strongly significant ($p < 0.05$). 
In this case, *log10(Area (km^2^))* is no longer a significant predictor, the reasons for this will be discussed later.

@@

```{r smoothsmodel6, echo = F, fig.cap="Visualisation of the smooth variables in the model, the shaded areas are the 95\\% confidence intervals associated with the fit of the smooth, the blue line is the mean smoothed relationship, with data plotted as individual points", out.width="90%"}
include_graphics("model6_smooths.png")
```

\newpage

@@

This last model has more explaining power with an adjusted *r^2^* of `r round(summary(model7)$r.sq,2)`. The results indicate that *Dryness* indicates a clear signifcant non-linear response where changes in forest cover in drier catchments having a greater impact on streamflow (Figure \@ref(fig:smoothsmodel7) and Table \@ref(tab:restrictlength)). Catchment area (*log10(Area (km^2^))*) also shows reasonable evidence of having an impact on flow with p = `r round(summary(model7)$s.table[2,4],2)`, and suggesting once again that changes in forest cover in larger catchments have less impact on streamflow. The variable *length* no longer is significant, after removal of the two studies with very long lengths.

@@

One concern with the result presented here, is that there are a few assessment techniques in the original dataset with a very low number of observations and this might skew the results of the analysis. This includes the category of Quasi paired watersheds and combinations of elasticity analysis and hydrological modelling (EA,HM) and paired watersheds and hydrological modelling (PWE,HM) (Table \@ref(tab:tableassess) and Figure \@ref(fig:assessment)).

### 2022-04-01 paper/Forest_and_Water/Forest_and_Water.tex
update funding
double spacing
fixed errors in pdf and added cover letter

@@

  \title{Factors determining how catchments respond to forest cover change. Re-analysing global data sets.}
    \author[DARE]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso}
   \ead{jalonso@fing.edu.uy} 
      \address[DARE]{ARC Training Centre Data Analytics for Resources and Environments \& Sydney Institute of Agriculture, School of Life and Environmental Sciences.}
    \address[The University of Sydney]{The University of Sydney, Sydney, NSW 2006, Australia}
    \address[INIA]{Project Manager, FPTA 358, Instituto Nacional de Investigacion Agropecuaria, INIA-Uruguay, Ruta 48 km 10, Rincon del Colorado, 90100 Canelones, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of Engineering, Universidad de la República, 11200 Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}

@@

@@

All the final data and analysis for this paper are located on github: \url{https://github.com/WillemVervoort/Forest_and_water} on the ``publish'' branch.

@@

This model explains more of the variance, but the improvement is marginal compared to the previous model with a adjusted \emph{r\textsuperscript{2}} of 0.39. This indicates that the categorical variables explain a limited amount of the overall variance in the change in flow data. However, it is interesting to note from Table \ref{tab:msix-linear} that several of the assessment methods are significant. In particular Paired Watersheds experiments (PWE), Hydrological modelling (HM) and Statistical techniques (SH) are strongly significant (\(p < 0.05\)).
In this case, \emph{log10(Area (km\textsuperscript{2}))} is no longer a significant predictor, the reasons for this will be discussed later.

\textbackslash begin\{figure\}
\includegraphics[width=0.9\linewidth]{model6_smooths} \textbackslash caption\{Visualisation of the smooth variables in the model. The shaded areas are the 95\% confidence intervals associated with the fit of the smooth, the blue line is the mean smoothed relationshiop. The data are plotted as individual points\}\label{fig:smoothsmodel6}
\textbackslash end\{figure\}

@@

This last model has more explaining power with an adjusted \emph{r\textsuperscript{2}} of 0.28. * The results indicate that \emph{Dryness} indicates a clear signifcant non-linear response where changes in forest cover in drier catchments having a greater impact on streamflow (Figure \ref{fig:smoothsmodel7}). Catchment area (\emph{log10(Area (km\textsuperscript{2}))}) also shows reasonable evidence of having an impact on flow with p = 0.07, and suggesting once again that changes in forest cover in larger catchments have less impact on streamflow. The variable \emph{length} no longer is significant, after removal of the two studies with very long lengths.

@@

One concern with the result presented heer, is that there are a few assessment techniques in the original dataset with a very low number of observations and this might skew the results of the analysis. This includes the category of Quasi paired watersheds and combinations of elasticity analysis and hydrological modelling (EA,HM) and paired watersheds and hydrological modelling (PWE,HM) (Table \ref{tab:tableassess} and Figure \ref{fig:assessment}).

@@

>>>>

\usepackage{setspace}

@@

  \title{Factors determining how catchments respond to forest cover change. Re-analysing global data sets.}
    \author[DARE]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi}
   \ead{eliananervif@gmail.com} 
    \author[IMFIA]{Jimena Alonso}
   \ead{jalonso@fing.edu.uy} 
      \address[DARE]{ARC Training Centre Data Analytics for Resources and Environments \& Sydney Institute of Agriculture, School of Life and Environmental Sciences.}
    \address[The University of Sydney]{The University of Sydney, Sydney, NSW 2006, Australia}
    \address[INIA]{Project Manager, FPTA 358, Instituto Nacional de Investigacion Agropecuaria, INIA-Uruguay, Ruta 48 km 10, Rincon del Colorado, 90100 Canelones, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of Engineering, Universidad de la República, 11200 Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}

@@

\doublespacing

@@

All the final data and analysis for this paper are located on github:\\
\href{https://github.com/WillemVervoort/Forest_and_water/tree/publish}{https://github.com/WillemVervoort/Forest\_and\_water} on the ``publish'' branch.

@@

This model (Tables \ref{tab:msix-linear} and \ref{tab:msix-smooth}) explains more of the variance, but the improvement is marginal compared to the previous model with a adjusted \emph{r\textsuperscript{2}} of 0.39. This indicates that the categorical variables explain a limited amount of the overall variance in the change in flow data. However, it is interesting to note from Table \ref{tab:msix-linear} that several of the assessment methods are significant. In particular Paired Watersheds experiments (PWE), Hydrological modelling (HM) and Statistical techniques (SH) are strongly significant (\(p < 0.05\)).
In this case, \emph{log10(Area (km\textsuperscript{2}))} is no longer a significant predictor, the reasons for this will be discussed later.

\begin{figure}
\includegraphics[width=0.9\linewidth]{model6_smooths} \caption{Visualisation of the smooth variables in the model, the shaded areas are the 95\% confidence intervals associated with the fit of the smooth, the blue line is the mean smoothed relationship, with data plotted as individual points}\label{fig:smoothsmodel6}
\end{figure}

\newpage

@@

This last model has more explaining power with an adjusted \emph{r\textsuperscript{2}} of 0.28. The results indicate that \emph{Dryness} indicates a clear signifcant non-linear response where changes in forest cover in drier catchments having a greater impact on streamflow (Figure \ref{fig:smoothsmodel7} and Table \ref{tab:restrictlength}). Catchment area (\emph{log10(Area (km\textsuperscript{2}))}) also shows reasonable evidence of having an impact on flow with p = 0.07, and suggesting once again that changes in forest cover in larger catchments have less impact on streamflow. The variable \emph{length} no longer is significant, after removal of the two studies with very long lengths.

@@

One concern with the result presented here, is that there are a few assessment techniques in the original dataset with a very low number of observations and this might skew the results of the analysis. This includes the category of Quasi paired watersheds and combinations of elasticity analysis and hydrological modelling (EA,HM) and paired watersheds and hydrological modelling (PWE,HM) (Table \ref{tab:tableassess} and Figure \ref{fig:assessment}).

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This work was funded through project FPTA 358, Instituto Nacional de Investigacion Agropecuaria, INIA-Uruguay.
